%----------------带星号一级标题标记------------	
\chapter*{\markboth{Abstract}{Abstract}Abstract}	
The image blur and jitter caused by aero-optical effect will greatly affect the the imaging quality and the guidance precision with the increase of the speed of the aircraft in the field of guidance. But the requirements of target guidance and tracking are getting higher and higher. Therefore, it is becoming more and more urgent of studying the physical mechanisms of turbulent flow around the high-speed aircraft and the optical transmission characteristics in the flow.

The research background and significance of the aero-optical effect of the high-speed flow were firstly introduced in this paper. The work of the predecessors was summarized through reviewing the development of the theory, experiment and numerical simulation of aero-optics. This article analyzed two main methods of numerical simulation, which were Large eddy simulation and Reynolds averaged simulation, according to the analysis of the mechanism of high-speed flow field. Shear stress transfer  computational model was derived based on the standard $k-\varepsilon$ and $k-\omega$ two equations turbulence model. Established the three-dimensional models of missile and airborne optical turret width ICEM modeling software. The numerical simulation and the results of the flow field around the missile and the optical turret were carried out based on the discrete governing equation and the fixed solution condition. The optical effects of the time averaged flow field and turbulent flow field were analyzed by means of ray tracing and statistical optics.Many evaluation methods of aero-optical effect were derived according the theory of optical transmission and the numerical simulation of the flow field was converted to optical parameters by using Gladstone-Dale's law. Based on the Mathematica numerical calculation, this article analyzed the wavefont distortion and strehl ratio generated by the beam while passing through the flow field. The distortion of the gaussian beam passing through the flow around the turrent while travelling with twice speed of the sound was studied by using optical transfer function.It was found that the intensity of the spot was obviously weakened and accompanied by a small deviation, and the distribution of the light field was no longer satisfied with the gaussian distribution.

\vspace{2em}{\bf\noindent Key words：}~~ aero-optics, turbulence, computational fluid dynamics, two equation model, optical transfer function, strehl ratio